---
title: "The Binomial Package"
author: "Jonathan Isaac"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r}
library("binomial")
```

## The Binomial Distribution

The most common discrete probability distribution, most often exemplified by a series of coin flips. This package allows a user to explore important questions like, "What are the odds of flipping a fair coin heads 3 out of 4 tosses?"

## Answering the question

Quickly lets answer this question before moving on to more spectacular things.

```{r}
bin_probability(success = 3, trials = 4, prob = .5)
```

So as you can see, specifying `success` for the amount of successful results, `trials` the number of trials, and `prob` the porbability of the successful outcome, we can answer any such question.

## Seeing results visually
 
We can see the answers to a wide variety of these kinds of questions, if we graph them!

```{r}
dist <- bin_distribution(100, .5)
plot.bindis(dist)
```

As well, we can see the probability of getting more or fewer than a certain amount of successes.

```{r}
cumu <- bin_cumulative(100, .5)
plot.bincum(cumu)
```

## More data

We can see detailed info on these distributions using bin_variable and summary.binvar, 
where the output of bin_variable is an input to summary.binvar.

```{r}
vars <- bin_variable(100, .5)
summary.binvar(vars)
```



